Compositional equivalences based on Open pNets

### 2020-06-11 2016-Weak-FH-Bisim/WeakBisim.tex
assignments
updated pNet code in appendix D

\subsection{Open Automata}
 Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values). 
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} (OT) over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J'}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action of this open transition.
%        We call \emph{source variables} of an OT the union of all variables
%        in the different terms
%        $\beta_j$ and $\alpha$, and the state variables of $s$.
        \Pred\ is a predicate over the  variables in $V$ and all variables
        in the different terms
       $\beta_j$ and $\alpha$. \Post\ is a set of 
	assignments that are effective after the open transition, they are
        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
        over the variables $V$ and all variables
        in the different terms
       $\beta_j$ and $\alpha$. Because the variables in $V$ can be in both side of the assignments, the assignments are always applied in a parallel manner. Open transitions are identified
        modulo logical equivalence on their predicate. 
\end{definition}

@@

pLTS M1
initial a0 
vars ?msg:Data

state a0
transition in(msg) -> a1 {a1_msg:=msg, m1_ec:=0}

state a1
vars a1_msg:Data m1_ec:Int
transition out(a1_msg, m1_ec) -> a0
transition synchro($tau)  -> a1 {m1_ec:=m1_ec+1}

@@

pLTS M1
  initial a0
  vars ?msg:Data ?c:Int

state a0
transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_ec:=c}

state a1
vars a1_msg:Data a1_ec:Int
transition m_send(a1_msg, a1_ec) -> a0 
transition synchro($tau) -> a2

state a2
transition $m_error -> a0

pLTS Sender
  initial s0
  vars ?msg:Data

state s0
transition s_recv(msg) -> s1 {s1_msg:=msg, s1_ec:=0}

state s1
vars s1_msg:Data s1_ec:Int
transition s_send(s1_msg, s1_ec) -> s2 {s2_ec:=s1_ec}

state s2
vars  s2_ec:Int
transition $s_ack -> s0
transition $s_error -> s1 {s1_ec:=s2_ec+1}

pLTS Receiver
  initial r0
  vars ?msg:Data ?c:Int

state r0
transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_ec:=c}

state r1
vars r1_msg:Data r1_ec:Int
transition r_send(r1_msg, r1_ec) -> r2

@@

\TODO{To be updated completely}

>>>>

\subsection{Open Automata}
 Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values). 
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} (OT) over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J'}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action of this open transition.
%        We call \emph{source variables} of an OT the union of all variables
%        in the different terms
%        $\beta_j$ and $\alpha$, and the state variables of $s$.
        \Pred\ is a predicate over the  variables in $V$ and all variables
        in the different terms
       $\beta_j$ and $\alpha$. \Post\ is a set of 
	assignments that are effective after the open transition, they are
        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
        over the variables $V$ and all variables
        in the different terms
       $\beta_j$ and $\alpha$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
        modulo logical equivalence on their predicate. 
\end{definition}

@@

pLTS M1
initial a0 
vars ?msg:Data
vars m_msg:Data m_ec:Int

state a0
transition in(msg) -> a1 {m_msg:=msg, m_ec:=0}

state a1
transition out(m_msg, m_ec) -> a0
transition synchro($tau)  -> a1 {m_ec:=m_ec+1}

@@

pLTS M1
  initial a0
  vars ?msg:Data ?c:Int
%vars a1_msg:Data a1_ec:Int
vars m_msg:Data m_ec:Int

state m0
transition m_recv(msg,c) -> m1 {m_msg:=msg, m_ec:=c}

state m1
transition m_send(m_msg, m_ec) -> m0 
transition synchro($tau) -> m2

state m2
transition $m_error -> m0

pLTS Sender
  initial s0
  vars ?msg:Data
%vars s1_msg:Data s1_ec:Int
%vars  s2_ec:Int
vars  s_msg:Data s_ec:Int

state s0
transition s_recv(msg) -> s1 {s_msg:=msg, s_ec:=0}

state s1
transition s_send(s_msg, s_ec) -> s2

state s2
transition $s_ack -> s0
transition $s_error -> s1 {s_ec:=s_ec+1}

pLTS Receiver
  initial r0
  vars ?msg:Data ?c:Int
%vars r1_msg:Data r1_ec:Int
vars r_msg:Data r_ec:Int

state r0
transition r_recv(msg,c) -> r1 {r_msg:=msg, r_ec:=c}

state r1
transition r_send(r_msg, r_ec) -> r2

@@

\TODO{To be updated completely, or removed ???}
